---
title: 'Pitch: CO2 Emissions Explorer'
author: "Afnan Khan"
date: "June 15, 2025"
output:
  html_document:
    df_print: paged
  ioslides_presentation:
    widescreen: true
    transition: faster
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(gapminder)
library(dplyr)
```

## Overview | Created on June 15, 2025

- **App Name**: CO2 Emissions Explorer
- **Purpose**: Visualize historical CO2 emissions and predict future trends for any country.
- **Why It’s Cool**: Interactive, user-friendly, and educational!
- **Link**: [Deployed on shinyapps.io](#) (https://etr80a-afnan-khan.shinyapps.io/CO2-Emissions/)

## How It Works

- **Input**: 
  - Select a country from a dropdown menu.
  - Adjust the year range with a slider.
- **Output**: 
  - Interactive plot showing historical CO2 emissions (blue) and a 10-year prediction (red).
- **Data**: Uses the `gapminder` R package (gdpPercap as a proxy for CO2).

## Sample Visualization

```{r sample_plot}
data <- gapminder %>% filter(country == "Canada", year >= 1950, year <= 2007)
data$co2 <- data$gdpPercap / 1000
ggplot(data, aes(x = year, y = co2)) +
  geom_line(color = "blue") +
  labs(title = "Sample: Canada CO2 Emissions", x = "Year", y = "CO2 (Metric Tons)") +
  theme_minimal()
```

## Why Use It?

- **Educational**: Learn about CO2 trends across countries.
- **Interactive**: Adjust inputs to explore different scenarios.
- **Simple**: No advanced knowledge required—just select and view!
- Try it at: [Shiny App Link](#) (https://etr80a-afnan-khan.shinyapps.io/CO2-Emissions/).

## Get Started

1. Visit the app on shinyapps.io.
2. Choose a country and year range.
3. Explore the plot and hover for details.
4. Source code: [GitHub Repository](#) (https://github.com/2Cloud-S/co2-explorer).
5. Built on June 15, 2025, with Shiny and R.
